---
title: "Lab 2"
author: "Fan Zhu"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

## Shell command

In this repo is a zip file named `organize_me.zip`. It can by unzipped by
running `unzip("organize_me.zip")`. Do this in your console so you only unzip
the folder once and not each time you knit the Rmd file.

The files in `organize_me/` contain a sample of various files you may have if 
you run a simulation on a high performance computer. Although, they are
currently disorganized. Organize the contents in `organize_me/` using the 
command line according to the following steps.

1. delete all `.input2` files. `rm *.input2'
2. remove the `flags/` directory and all of its contents. 'rm -r flags'
3. place the test data text files in a directory named `test_data/`.
'mkdir test_data', 'mv testdata*.txt test_data'
4. place the `.sh` files in a directory named `scripts_shell/`.
'mkdir scripts_shell', 'mv *.sh scripts_shell'
5. place the `.R` files in a directory named `scripts_R/`.
"mkdir scripts_R", "mv *.R scripts_R"
6. place the `.qsub` files in a directory named `hpc_start/`.
'mkdir hpc_start', 'mv *.qsub hpc_start'
7. copy directory `organize_me/` and name the copy `simulations/`.
'cd -', 'cp -R organize_me simulations'
8. delete directory `organize_me/` and all of its contents.
"rm -R organize_me"


## Attributes

Create a date-time object based on the atomic double vector below. You'll
need to set the class attribute to `"POSIXct"`

```{r}
z <- seq(0, 3600 * 10, by = 3600)
as.POSIXct(z, origin = "1960-01-01")  

```

What do you notice about the date-time? If you are unsure, check out
Unix Epoch.

## Subsetting

Consider the atomic vector `x`.

```{r}
set.seed(0826) # set seed to ensure reproducibility
x <- sample(x = c(letters, -15:15), size = 50, replace = TRUE)
x
```

1. subset only the letters from `x`.
```{r}
grep('^[A-Za-z ]+$', x, value = TRUE)
grep('^[A-Za-z ]+$', x, value = FALSE)
```


2. subset only the negative numbers from `x`.
```{r}
grep('^[A-Za-z ]+$', x, value = TRUE)
```


3. select the numbers divisible by 3 from `x`.


4. remove all values with an even index from `x`.


